### 2018-05-26 Paper/disc.tex
...

Parameter screening methodology was implemented to low-to-moderate dimensional test problems
and an accurate ROS was constructed to demonstrate potential for computational gains in
each case. Furthermore, the overall framework was implemented  to a relatively higher 
dimensional application involving kinetics of the H$_2$/O$_2$ reaction mechanism. 
Significant dimension reduction was accomplished for two different scenarios involving
a fuel-rich and a fuel-lean mixture. In both cases, the resulting ROS was able to capture
the input-output relationship as well as the uncertainty in the quantity of interest with 
reasonable accuracy. Additional highlights and limitations of the proposed framework are as follows:

\begin{enumerate}
\item The proposed framework is agnostic to the choice of the surrogate although PCE's were used
in this work. 
\item The scope for dimension reduction and associated computational gains are
dependent upon the application as well as the quantity of interest. 
\item The quantity of interest must be differentiable with respect to each uncertain parameter
to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving compute-intensive
simulations even if the scope for dimension reduction is small and vice versa. Hence, careful judgment 
is required when implementing the framework. 
\item Exponential gains can be realized in situations where multiple surrogates need to be
constructed as illustrated in the kinetics application. Other possible scenarios 
include inverse problems involving parameter estimation in a Bayesian setting. 
\end{enumerate}

>>>>

Parameter screening methodology was implemented to low-to-moderate dimensional test problems
and an accurate ROS was constructed to demonstrate potential for computational gains in
each case. Furthermore, the overall framework was implemented  to a relatively higher 
dimensional application involving kinetics of the H$_2$/O$_2$ reaction mechanism. 
Significant dimension reduction was accomplished for two different scenarios involving
a fuel-rich and a fuel-lean mixture. In both cases, the resulting ROS was able to capture
the input-output relationship as well as the uncertainty in the quantity of interest with 
reasonable accuracy. Additional highlights and limitations of the proposed framework are as follows:
\alennote{This is unclear: if we list limitations, we should be specific and
not mix them with highlights;
as for limitations, we can mention 
e.g., we do not account for correlations, and our method applies only to 
models with differentiable dependence on parameters, etc.; I would not make
a bulleted list; I would briefly discuss the limitations, and if possible turn 
them into strengths! e.g., we consider uncorrelated parameters, but that's okay as in 
many cases correlations are not well understood and assuming independence is reasonable, etc.}
\begin{enumerate}
\item The proposed framework is agnostic to the choice of the surrogate although PCE's were used
in this work. 
\item The scope for dimension reduction and associated computational gains are
dependent upon the application as well as the quantity of interest. 
\item The quantity of interest must be differentiable with respect to each uncertain parameter
for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving compute-intensive
simulations even if the scope for dimension reduction is small and vice versa. Hence, careful judgment 
is required when implementing the framework. 
\item Exponential gains can be realized in situations where multiple surrogates need to be
constructed as illustrated in the kinetics application. Other possible scenarios 
include inverse problems involving parameter estimation in a Bayesian setting. 
\end{enumerate}
